The problem and promise of scale in multilayer networks

### 2020-01-22 paper/manuscript.Rmd
Update manuscript.Rmd

### Landscape data and habitat classification
Landscape classification data were provided by the Newfoundland and Labrador Wildlife Division. Available landcover classification included nine habitat types at 30 x 30m resolution. We distilled the landcover types into three broad categories: foraging habitat, open habitat, and closed habitat. Foraging habitat consisted of lichen habitat, open habitat consisted of wetland, rocky barrens, frozen lakes, and anthropogenic habitat types, while closed habitat consisted of coniferous forest, conifer scrub, broadleaf forest, and mixed-wood forest habitat types.

### Generating multilayer social networks
We used R package spatsoc (Robitaille et al. 2019) in *R version* (R CITATION) to generate proximity-based social network layers from GPS telemetry data (see above). We generated monolayer association networks for caribou in each habitat and season based on proximity of GPS fixes for individual caribou: we assumed association between two individuals if simultaneous GPS fixes (i.e., recorded within 5 minutes of each other) were within 50 m of one another (Lesmerises et al. 2018). We represented individuals in our networks by nodes and associations between individuals were represented by edges.

@@

To assess the influence of landcover scale on multilayer networks, we re-sampled our landcover classification map at varying scales. Specifically, we selected scales relevant to caribou ecology. We re-sampled landcover using the **`grainchanger` package[???]** at five scales: 100m, 250m, 500m, 1000m, 2500m. Sampling at 100 and 250m represents fine-scale decision making for caribou during foraging (REF), while re-sampling at 1000m and 2500m represents the scale at which caribou tend to select and avoid habitat (Bastille-Rousseau et al. 2017). represents the local foraging Resampling method was modal moving window. Water areas were masked before resampling. Landcover reclassified to open, forest and lichen.

```
open <- c(1, 6, 7, 9)
forest <- c(2, 3, 4, 5)
lichen <- 8
```

Each modal landcover, and the original are sampled and separate network layers constructed for each.

1. spatial threshold

Social networks constructed using spatsoc. Multilayer networks constructed for each season. Variable modified is the spatial buffer. Series from 5 to 500.

1. number of observations

>>>>

### Landscape data and habitat classification
Landscape classification data were provided by the Newfoundland and Labrador Wildlife Division. Available landcover classification included nine habitat types at 30 x 30m resolution. We distilled the landcover types into three broad categories: foraging habitat, open habitat, and closed habitat. Foraging habitat consisted of lichen habitat, open habitat consisted of wetland, rocky barrens, and anthropogenic habitat types, while closed habitat consisted of coniferous forest, conifer scrub, broadleaf forest, and mixed-wood forest habitat types. Water habitat was excluded from all subsequent analyses.

```
open <- c(1, 6, 7, 9)
forest <- c(2, 3, 4, 5)
lichen <- 8
```
### Generating multilayer social networks
We used R package spatsoc (Robitaille et al. 2019) in *R version* (R CITATION) to generate proximity-based social network layers from GPS telemetry data (see above). We generated monolayer association networks for caribou in each habitat and season based on proximity of GPS fixes for individual caribou: we assumed association between two individuals if simultaneous GPS fixes (i.e., recorded within 5 minutes of each other) were within 50 m of one another (Lesmerises et al. 2018). We represented individuals in our networks by nodes and associations between individuals were represented by edges.

@@

To assess the influence of landcover scale on multilayer networks, we re-sampled our landcover classification map at varying scales. Specifically, we selected scales relevant to caribou ecology. We re-sampled landcover using the **`grainchanger` package/function[???]** (REF) at five scales: 100m, 250m, 500m, 1000m, 2500m. Sampling at 100 and 250m represents fine-scale decision making for caribou during foraging (REF), while re-sampling at 1000m and 2500m represents the scale at which caribou tend to select and avoid habitat (Bastille-Rousseau et al. 2017). Resampling occurred based on a modal moving window method, where XXXXX.

**Each modal landcover, and the original are sampled and separate network layers constructed for each. [QW: NOT SURE WHAT THIS MEANS]**

#### Altering social scale

Social networks constructed using spatsoc (Robitaille et al. 2019). Multilayer networks constructed for each season. Variable modified is the spatial buffer. Series from 5 to 500.

#### Altering the number of observations
